Bioverse: Potentially Observable Exoplanet Biosignature Patterns Under the UV Threshold Hypothesis for the Origin of Life

### 2025-02-14 src/tex/ms.tex
link back to discussion on priors

\subsection{Contextual support for potential biosignature detections} % corresponds to ... which conclusion?
The predicted interplay of \gls{NUV} flux and \gls{HZ} occupancy in enabling abiogenesis via the cyanosulfidic scenario could in principle be used to add or remove credibility from a tentative biosignature detection.
For example, with a strong belief that this scenario is the only viable one for the origins of life, a biosignature detection on a planet orbiting a strongly UV-radiating star may add credibility to the detection.
Conversely, a biosignature detection on a planet estimated to have received very little UV~radiation would increase the likelihood of a false positive detection.
On the other hand, should the detection in the latter case be confirmed, it could be used to falsify the UV~Threshold Hypothesis.

@@

\rev{
\subsubsection{Bayesian Evidence and the Influence of Priors}
Our semi-analytical analysis (Section~\ref{sec:results-semianalytical}) employs Bayes factors to quantify the evidence in favor of or against the UV~Threshold Hypothesis that future observations may provide.
%In contrast to frequentist p-value tests, which only assess the likelihood of the null hypothesis, this approach explicitly incorporates the likelihood of the alternative hypothesis.
%However, Bayes factor analysis limits the scope to two competing hypotheses, and it does not estimate posterior probabilities.
}

>>>>

\subsection{Contextual support for potential biosignature detections} % corresponds to ... which conclusion?
The predicted interplay of \gls{NUV} flux and \gls{HZ} occupancy in enabling abiogenesis via the cyanosulfidic scenario could in principle be used to add or remove credibility from a tentative biosignature detection.
For example, with a strong \rev{prior} belief that this scenario is the only viable one for the origins of life \rev{(see Section~\ref{sec:discussion-bayes})}, a biosignature detection on a planet orbiting a strongly UV-radiating star may add credibility to the detection.
Conversely, a biosignature detection on a planet estimated to have received very little UV~radiation would increase the likelihood of a false positive detection.
On the other hand, should the detection in the latter case be confirmed, it could be used to falsify the UV~Threshold Hypothesis.

@@

\rev{
\subsubsection{Bayesian Evidence and the Influence of Priors}\label{sec:discussion-bayes}}
Our semi-analytical analysis (Section~\ref{sec:results-semianalytical}) employs Bayes factors to quantify the evidence in favor of or against the UV~Threshold Hypothesis that future observations may provide.
%In contrast to frequentist p-value tests, which only assess the likelihood of the null hypothesis, this approach explicitly incorporates the likelihood of the alternative hypothesis.
%However, Bayes factor analysis limits the scope to two competing hypotheses, and it does not estimate posterior probabilities.
}
